---
title: "Capstone Proposal"
author: "David Aragon"
date: "January 9, 2018"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r}
autos_csv <- read.csv("~/Downloads/autos (1).csv")
carPrice <- read.csv("~/Downloads/cnt_km_year_powerPS_minPrice_maxPrice_avgPrice_sdPrice.csv")
```

## Capstone Proposal Overview

The used car market lately has been on the rise. With the economy benefiting from lower unemployment rates, the used car market has flourished. The car market has a whole has benefited as well with lease sales increasing. Because lease sales are on the rise, people can either turn in their vehicle or keep it. For those that have kept their vehicle, the used car market gains from consumer turn ins. Consumers that leased their vehicle are much more likely to take care of their vehicles to avert paying high wear and tear charges. As a result, the quality of used cars in a particular car lot is quite good. 


## Problem
In my analysis, I want to be able to forecast and display the used car marke based on already used data. The problem I want to solve is eliminating cars that will not sell in a timely manner 

## Who is my client and Why do they care

My client will be finance companies looking to forecast, purchase and/or sell vehicles in and out of their respective lots. 

## Data

The data used in this analy/ ccvcv  fsis will be scraped from Ebay-Kleinanzeigan. These data sets include vehicle information, seller, notRepaired Damage, #ofpictures, lastSeeenOnline, averagePrice, lowPrice, highPrice.

#### Autos.CSV data set

This dataset's summary is the following:
```{r auto, echo = FALSE}
summary(autos_csv)

```

This dataset's structure is the following:
```{r}
str(autos_csv)


```

In review of this dataset, some of the fields are in german. I will have to translate those field into English for my clients. The rest of the data looks to be in fair order and will be an easy import for further analysis 

#### Car Prices data sets

This dataset's summary is the following:
```{r echo = FALSE }
summary(carPrice)

```

This dataset's structure is the following:
```{r echo= FALSE }
str(carPrice)
```

In this dataset, it has 8 variables : count, year, km, powerPS, minPrice, maxPrice, avgPrice, and sdPrice. 6 of these variable are integer types and 2 are numeric types. This dataset is fairly clean so not much clean up will be involved in data analysis. 

## Approach

My approach to analyzing this data will be to clean up the data significantly. The data is in german so I will need to translate as my client will be mostly english speakers. Once data is cleaned, I will join the datasets are prices and vehicle info are two different datasets. Using R language and RStudio, I will display which vehicle are the best selling and also display a table of value loss of an average used car per year. 

## Deliverables

I plan on using R language to write the necessary code to display line graphs to show the progression or regression of certain vehicle in a particular lot. I plan on converting this visualization as a PDF file to share with client

